### 2019-09-12 manuscript.tex
Add LaTex templates and fill in affiliation

\documentclass[a4,center,fleqn]{NAR}

% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

%\articlesubtype{This is the article type (optional)}

\begin{document}

\title{Faithful short read mapping with Sesame}

\author{%
Ruggero Cortini\,$^{1}$,
Eduard Valera Zorita\,$^{1}$,
Guillaume J. Filion\,$^{1,2,3}$
\footnote{To whom correspondence should be addressed.
Email: guillaume.filion@gmail.com}}

\address{%
$^{1}$Center for Genomic Regulation (CRG), The Barcelona Institute
of Science and Technology, Dr. Aiguader 88, Barcelona 08003, Spain;
$^{2}$University Pompeu Fabra (UPF), Barcelona, Spain;
$^{3}$present address: Department of Biological Sciences, University
of Toronto Scarborough, Toronto, ON, Canada.}
% Affiliation must include:
% Department name, institution name, full road and district address,
% state, Zip or postal code, country

\history{%
Received January 1, 2009;
Revised February 1, 2009;
Accepted March 1, 2009}

\maketitle

\begin{abstract}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text.
\end{abstract}

\section{Introduction}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.
Text \cite{1}.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
\begin{align*}
&\mathrm{Ascorbate} + \mathrm{EDTA} \cdot \mathrm{Fe}^{3+} \to
\hbox{Oxidized ascorbate}
\\
&\mathrm{EDTA} \cdot \mathrm{Fe}^{2+} + \mathrm{H}_2
\mathrm{O}_2 \to
\mathrm{EDTA} \cdot \mathrm{Fe}^{3+} + \cdot
\mathrm{OH} + \mathrm{OH}^-
\end{align*}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
% **************************************************************
% Keep this command to avoid text of first page running into the
% first page footnotes
\enlargethispage{-65.1pt}
% **************************************************************

Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.
Text \cite{2,3}.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text.
Text \cite{4}.

\section{MATERIALS AND METHODS}

\subsection{Materials subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsubsection{Materials subsubsection one.}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text:
\begin{align}
\mathrm{LD}^r = \frac{\mathrm{LD}}{A_\mathrm{iso}}
= 1.5 S \left( 3 \cos^2 \alpha_i - 1 \right)
\end{align}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsection{Materials subsection two}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text
(see Figure \ref{NAR-fig1}).

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.
\begin{equation*}
\mathrm{LD} \left( t \right) =
\sum\limits_i
a_i \exp \left( \frac{-t}{\tau_i} \right)
\end{equation*}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.

\begin{figure}[t]
\begin{center}
\includegraphics{NAR-fig1.eps}
\end{center}
\caption{Caption for figure within column.}
\label{NAR-fig1}
\end{figure}

\section{RESULTS}

\subsection{Results subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.

\begin{table}[b]
\tableparts{%
\caption{This is a table caption}
\label{table:01}%
}{%
\begin{tabular*}{\columnwidth}{@{}lllll@{}}
\toprule
Col. head 1 & Col. head 2 & Col. head 3 & Col. head 4 & Col. head 5
\\
& (\%) & (s$^{-1}$) & (\%) & (s$^{-1}$)
\\
\colrule
Row 1 & Row 1 & Row 1 & -- & --
\\
Row 2 & Row 2 & Row 2 & Row 2 & Row 2
\\
\botrule
\end{tabular*}%
}
{This is a table footnote}
\end{table}

\subsection{Results subsection two}

Text.  Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Table \ref{table:01}).

Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Figure \ref{NAR-fig2}a).

Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\begin{figure*}[t]
\begin{center}
\includegraphics{NAR-fig2.eps}
\end{center}
\caption{Caption for wide figure over two columns.
\textbf{(a)} Left figure.
\textbf{(b)} Right figure (see (a)).
}
\label{NAR-fig2}
\end{figure*}

\subsection{Results subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

\section{DISCUSSION}

\subsection{Discussion subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection two}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

\subsection{Discussion subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.

\section{CONCLUSION}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

\section{ACKNOWLEDGEMENTS}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.

\subsubsection{Conflict of interest statement.} None declared.
\newpage

\begin{thebibliography}{4}

% Format for article
\bibitem{1}
Author,A.B. and Author,C. (1992)
Article title.
\textit{Abbreviated Journal Name}, \textbf{5}, 300--330.

% Format for book
\bibitem{2}
Author,D., Author,E.F. and Author,G. (1995)
\textit{Book Title}.
Publisher Name, Publisher Address.

% Format for chapter in book
\bibitem{3}
Author,H. and Author,I. (2005)
Chapter title.
In
Editor,A. and Editor,B. (eds),
\textit{Book Title},
Publisher Name, Publisher Address,
pp.\ 60--80.

% Another article
\bibitem{4}
Author,Y. and Author,Z. (2002)
Article title.
\textit{Abbreviated Journal Name}, \textbf{53}, 500--520.

\end{thebibliography}

\end{document}

### 2019-09-17 manuscript.tex
First draft of the introduction

@@
 
-\title{Faithful short read mapping with Sesame}
+\title{Faithful short-read mapping with Sesame}
 
 \author{%
-Ruggero Cortini\,$^{1}$,
-Eduard Valera Zorita\,$^{1}$,
+Ruggero Cortini\,$^{1,\text{\#}}$,
+Eduard Valera Zorita\,$^{1,\text{\#}}$,
 Guillaume J. Filion\,$^{1,2,3}$
@@
 $^{3}$present address: Department of Biological Sciences, University
-of Toronto Scarborough, Toronto, ON, Canada.}
+of Toronto Scarborough, Toronto, ON, Canada; $^{\text{\#}}$ equal
+contributions.}
 % Affiliation must include:
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text.
-Text \cite{1}.
+High throughput DNA sequencing is now a standard technology in the
+academia and in the industry, with countless applications in diagnosis,
+forensics, surveillance and research \cite{1}. The Illumina short-read
+technology currently dominates the market of DNA sequencing, making the
+associated software an important target for optimization.
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+The standard way to identify a read is to map it to a known reference
+sequence, typically a genome. Work on short-read mappers has been
+traditionally focused on improving the speed, reducing the memory
+footprint and increasing the accuracy. Another important focus has been to
+develop variations to address the actual needs of the user, as different
+problems often entail different read types (e.g., compare CHiP-seq and
+Hi-C).
+
+Meanwhile, progress has been more limited on another aspect of the mapping
+process: \emph{faithfulness}. Mapping algorithms are heuristics, so there
+is always a chance that the proposed location of a read is wrong.
+Faithfulness is the capacity to correctly estimate this probabilty.
+Importantly, one can reduce the probability of errors without having to
+measure it, so accuracy and faithfulness are usually unrelated.
+
+The importance of faithfulness is recognized in the specifications of the
+SAM format \cite{1} that include a \emph{mapping quality} score. The
+standard defines it as $-10 \cdot \log_{10}Pr$\{mapping position is
+wrong\}, but some mappers use a qualitative scale (e.g., STAR), and
+some others do not compute it (e.g., GEM). As for the mappers that comply
+with the SAM standard, the scores are undocumented, causing
+puzzlment and frustration\footnote{http://www.acgt.me/blog/2015/3/17/more-madness-with-mapq-scores-aka-why-bioinformaticians-hate-poor-and-incomplete-software-documentation}.
+
+Achieving faithful read mapping is a hard problem, for which this is
+presently no solution. Yet, this is an important challenge for the
+following reasons:
+$i$ in many applications it is essential to know the risk associated with
+every read (e.g., contaminated material such as ancient DNA);
+$ii$ a mapper is easier to use if error rates are what they claim to
+be;
+$iii$ good calibrations open opportunities to improve the speed-accuracy
+tradeoff.
+
+We recently proposed a strategy to compute the error rate of different
+seeding strategies used in short-read mappers \cite{1}. This strategy
+borrows some basic concepts from analytic combinatorics \cite{1} to
+develop a formal computation framework. Here we present a C implementation
+of this framework in a library called Sesame. We also develop a
+statistical method to estimate the parameters required to compute seeding
+probabilities. We demonstrate the feasibility of our approach by
+developing a naive mapper based on Sesame. Not only is this mapper
+faithful, but it also reveals the existence of ``super reads'' that can be
+mapped with much higher confidence than was previously thought possible.
+
 \begin{align*}

### 2019-09-19 manuscript.tex
Add text/figure mortal kombat MEM vs skip seeds

@@
 \begin{abstract}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text.
+Abstract will come later.
 \end{abstract}
@@
 is always a chance that the proposed location of a read is wrong.
-Faithfulness is the capacity to correctly estimate this probabilty.
+Faithfulness is the capacity to correctly estimate this probability.
 Importantly, one can reduce the probability of errors without having to
@@
 with the SAM standard, the scores are undocumented, causing
-puzzlment and frustration\footnote{http://www.acgt.me/blog/2015/3/17/more-madness-with-mapq-scores-aka-why-bioinformaticians-hate-poor-and-incomplete-software-documentation}.
+puzzlement and frustration\footnote{http://www.acgt.me/blog/2015/3/17/more-madness-with-mapq-scores-aka-why-bioinformaticians-hate-poor-and-incomplete-software-documentation}.
 
@@
 \end{align*}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
 % **************************************************************
@@
 
-\subsection{Results subsection one}
+\subsection{The Sesame library}
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text.
+% !! IMPORTANT !! %
+% Say something about the seeds. In particular, it is important to
+% mention that we do not do spaced seeds.
+
+We wrote a C library to compute seeding probabilities from the theoretical
+results presented in \cite{1}. Briefly, the strategy was to represent
+reads and off-target sequences in a custom combinatorial alphabet, specify
+the generating functions of basic words and define a language based on a
+transfer matrix. The powers of the transfer matrix contain the generating
+functions of the reads of interest, from which we can extract their
+probability of ocurrence.
+
+The probability that a read contains a seed depends on the problem and on
+the read. Sesame computes seeding probabilities from five user-specified
+parameters. The problem-specific parameters are known to the user and
+consist of the read length $k$, the error rate $p$ and the minimum seed
+size $\gamma$. The read-specific parameters are unknown to the user and
+consist of the number of duplicates of the target $N$, and their average
+sequence divergence $\mu$. We will explain below how to estimate them in
+practice.
+
+The Sesame library was built for performance so that it can be integrated
+in mapping frameworks. This means that computations are performed only
+once for a given set of parameters and memoized for later retrieval. The
+parameters $k$, $p$ and $\gamma$ are constant throughout the sequencing
+run, but $N$ and $\mu$ must be computed for every read. By default, Sesame
+collapses the $(N, \mu)$ pairs to a coarse grid of $15 \times 3=45$
+values. Computing all 45 values takes a few minutes on modern hardware,
+which is negligible compared to mapping a sequencing run with several
+million reads. In addition, the computed values can be saved on disk for
+reuse in later runs. The user interface and available options are further
+described on the main page of the repository.
+
+\subsection{Comparing seeding strategies}
+
+The seeding step is an essential part of read mapping. Choosing an
+appropriate strategy is important, but this is usually based on limited
+testing. With accurate seeding probabilities, it is possible to compare
+the merits of different seeding strategies, which can be useful for
+choosing a seed type or a minimum seed length.
+
+As an example, we compare the default strategies of BWA and Bowtie2 at 1\%
+sequencing error. Note that both mappers use advanced methods to refine
+the seeding heuristic, so the comparison does not reflect their
+performance. It is nevertheless useful to give a baseline for the
+potential of each strategy. The default strategy of BWA it to use MEM
+seeds of minimum size 19; that of Bowtie2 is to use seeds of size 16 every
+ten nucleotides (referred to here as skip-9 seeds).
+
+The worst seeding outcome is that the set of candidate loci contains only
+paralogues of target. In this case the target is lost, but worse, the
+mapper is on a wrong path and may return a paralogue instead. It is thus
+important to control the probability of this outcome referred to as
+off-target seeding.
+
+Figure~\ref{fig:mortal_kombat} shows the off-target probabilities computed
+by Sesame. Counter-intuitively, the probability initially increases with
+the read size for MEM seeds. It turns out that off-target MEM seeds are
+common in short reads that contain errors. Since longer reads have a
+higher chance of containing an error, the off-target rate initially
+increases. This effect dampens so that all the probabilities eventually
+decrease exponentially, albeit at different rates.
+
+For skip seeds, the off-target rates decrease in staircase with a drop
+every 10 nucleotides. Indeed, the seeds are exactly the same if the read
+length stays within the same decade. The curves show an overal linear
+trend and have the same asymptotic rate.
+
+From this we draw the important conclusion that the performance of skip
+seeds degrades much less than MEM seeds when the target contains
+paralogues. Skip seeds are thus better suited for sensitive mapping in
+repeated sequences. Figure~\ref{fig:mortal_kombat} also shows that the
+performance of skip seeds on this criterion is simply better than MEM
+seeds. However one has to bear in mind that we compare MEM seeds of size
+19 with skip seeds of size 16: the gain in sensitivity comes at the cost
+of a substantially larger candidate set. In practice the candidate set
+must be further filtered, so the final performance cannot be as high as
+suggested by Figure~\ref{fig:mortal_kombat}.
+
+Another interesting observation is that for MEM seeds, the off-target rate
+is above $10^{-3}$ for reads of 50 nucleotides or less, meaning that
+beating quality 30 is not straightforward in these conditions. It is
+important to remember that mapping cannot be wrong if the target has no
+paralogue (because it is trivial to recognize that false positives have no
+homology with the read). Therefore, the main strategy to reach high
+mapping confidence with MEM seeds is not to reduce the minimum seed size,
+but to ascertain that the target is a unique sequence. We will show how to
+do achieve this below.
+
+\section{Estimating parameters $N$ and $\mu$}
+
+A key component of...
 

### 2019-09-19 make_figure_mortal_kombat.R

@@ -1,0 +1,56 @@
+mem = log10(as.matrix(read.table("results_mem.txt")))
+skip = log10(as.matrix(read.table("results_skip.txt")))
+
+k = 20:160
+ylim = c(-10,0)
+
+pdf("mortal_kombat.pdf", height=6, width=12, useDingbats=FALSE)
+
+par(mfrow=c(1,2))
+par(mar=c(3.5,3.5,1.5,1.5))
+
+plot(k, mem[1,], type="n",
+   panel.first=grid(), ylim=ylim,
+   bty="n", xaxt="n", yaxt="n", xlab="", ylab="")
+lines(k, mem[1,], col="grey50", lwd=1.05)
+lines(k, mem[2,], col="grey45", lwd=1.10)
+lines(k, mem[3,], col="grey40", lwd=1.15)
+lines(k, mem[4,], col="grey35", lwd=1.20)
+lines(k, mem[5,], col="grey30", lwd=1.25)
+lines(k, mem[6,], col="grey25", lwd=1.30)
+lines(k, mem[7,], col="grey20", lwd=1.35)
+lines(k, mem[8,], col="grey15", lwd=1.40)
+lines(k, mem[9,], col="grey10", lwd=1.45)
+lines(k, mem[10,], col="grey5", lwd=1.50)
+
+title(xlab="Size (nt)", ylab="Off-target rate (log10)",
+   col.lab="grey25", line=2.2)
+axis(side=1, cex.axis=.8, col="grey50", col.axis="grey25")
+axis(side=2, cex.axis=.8, col="grey50", col.axis="grey25")
+
+legend(x="bottomleft", lwd=c(1.05, 1.10, 1.15, 1.20, 1.25, 1.30,
+   1.35, 1.40, 1.45, 1.50), col=c("grey50", "grey45", "grey40",
+   "grey35", "grey30", "grey25", "grey20", "grey15", "grey10", "grey5"),
+   legend=c("1","5","10","20","50","100","200","400", "750","1500"),
+   inset=.02, bg="white", box.col="white", text.col="grey25")
+
+plot(k, skip[1,], type="n",
+   panel.first=grid(), ylim=ylim,
+   bty="n", xaxt="n", yaxt="n", xlab="", ylab="")
+lines(k, skip[1,], col="grey50", lwd=1.05)
+lines(k, skip[2,], col="grey45", lwd=1.10)
+lines(k, skip[3,], col="grey40", lwd=1.15)
[…]

### 2019-09-20 manuscript.tex
Add estimation strategy and start super reads

@@
 paralogues. Skip seeds are thus better suited for sensitive mapping in
-repeated sequences. Figure~\ref{fig:mortal_kombat} also shows that the
-performance of skip seeds on this criterion is simply better than MEM
-seeds. However one has to bear in mind that we compare MEM seeds of size
-19 with skip seeds of size 16: the gain in sensitivity comes at the cost
-of a substantially larger candidate set. In practice the candidate set
-must be further filtered, so the final performance cannot be as high as
-suggested by Figure~\ref{fig:mortal_kombat}.
+repeated sequences. Incidentally, this Figure~\ref{fig:mortal_kombat}
+shows that it is suboptimal for a MEM-based mapper to all the candidate
+loci when there is more than a handful of them: if the target has more
+than 20 paralogues, the mapping quality will remain low even when the
+output is correct. A better strategy is to either bail out or switch to a
+more sensitive seeding method (BWA uses a re-seeding policy).
 
-Another interesting observation is that for MEM seeds, the off-target rate
-is above $10^{-3}$ for reads of 50 nucleotides or less, meaning that
-beating quality 30 is not straightforward in these conditions. It is
-important to remember that mapping cannot be wrong if the target has no
-paralogue (because it is trivial to recognize that false positives have no
-homology with the read). Therefore, the main strategy to reach high
-mapping confidence with MEM seeds is not to reduce the minimum seed size,
-but to ascertain that the target is a unique sequence. We will show how to
-do achieve this below.
+A related observation is that for MEM seeds, the off-target rate is above
+$10^{-3}$ for reads of 50 nucleotides or less, meaning that beating
+quality 30 is not straightforward in these conditions. It is important to
+remember that mapping cannot be wrong if the target has no paralogue
+(because it is trivial to recognize that false positives have no homology
+with the read). Therefore, the main strategy to reach high mapping
+confidence with MEM seeds is not to reduce the minimum seed size, but to
+ascertain that the target is a unique sequence. We will show how to do
+achieve this below.
 
-\section{Estimating parameters $N$ and $\mu$}
+Figure~\ref{fig:mortal_kombat} suggests that the performance of skip seeds
+is better than that of MEM seeds. However one has to bear in mind that we
+compare MEM seeds of size 19 with skip seeds of size 16: the gain in
+sensitivity comes at the cost of a larger candidate set. In practice such
+a large candidate set must be further filtered (Bowtie2 does this with a
+priority policy), so the final performance of skip seeds cannot be as high
+as suggested in the figure because of speed constraints.
 
-A key component of...
+\section{Estimating $N$ and $\mu$}
+
+Estimating the two read-dependent parameters $N$ and $\mu$ is essential to
+compute seeding probabilities. Recall that $N$ is the number paralogues of
+the target ($N=0$ means that it is unique) and that $\mu$ is the sequence
+divergence (the average fraction of mismatches between a paralogue and the
+target).
+
+The key observation is that the seeding algorithm can also reveal the
+paralogue structure of the target. Queries in the FM index are carried out
+using an algorithm known as the backward search. Extending the query one
+nucleotide at a time, the backward search returns the number of matching
+sequences in the genome. The decaying number of hits depends on how many
+paralogues of the target are present in the genome, and how similar they
+are with each other. It is thus possible to use the series of the backward
+search to estimate $N$ and $\mu$.
+
+Writing the likelihood of the process is straightforward if we assume that
+nucleotides are used uniformly at random in the genome. The difficulty is
+that the first iterations of the backward search are uninformative. For
+instance, a query of length 10 is expected to have $\geq 3000$ hits in
+the genome, so the potential paralogues of the target are hidden among so
+many random hits. In practice, we ignore the first iterations until the
+number of random hits is lower than 1. The information is labelled as
+missing and the likelihood is updated accordingly. This gives a function
+that can now by maximized with respect to $N$ and $\mu$.
+
+Initial simulations revealed that the maximum likelihood estimates of $N$
+and $\mu$ have a large variance. To mitigate this effect, we opted for a
+grid search where we test only plausible values of $\mu$ and compute the
+associated $N$ (see Methods). This gave a fast algorithm forced to produce
+reasonable estimates.
+
+We initially tested this method on the read, gathering the series of decay
+during the seeding process. However, we quickly realized that this method
+routinely missed paralogues because of sequencing errors. Using mapping as
+an error correction mechanism, we tested a prototype estimating $N$ and
+$\mu$ from the sequence of the best hit and obtained significantly better
+results, so we settle for this option, even though it is slower. It is of
+course possible that the best hit is not the target, but if it is a
+paralogue, the estimated values of $N$ and $\mu$ should be similar.
+
+The estimation strategy is depicted in Figure~\ref{fig:strategy}. The
+putative target is segmented in windows of 30 nucleotides overlapping by
+20 nucleotides. The grid search is run a every window in both the foward
+and reverse orientation, ignoring the first 20 iterations of the backward
+search. The windowing approach accomodates the fact that only some
+regions of the target may be repeated (e.g., if the read straddles a
+transposon). Finally, we take the median values of $N$ and $\mu$ as
+representative for the whole sequence.
+
+\section{Super reads}
+
+While testing the estimation algorithm on reads of size 50, we observed
+that a sub-population of them had mapping error rates below $10^{-5}$.
+This is surprising in regard of Figure~\ref{fig:mortal_kombat}a because in
+a genome where half of the sequences are duplicated, the error rate should
+be $\approx 1/2 10^{-3}$. We reasoned that non-repeated sequences must be
+overrepresented in this sub-population of reads.
+
+Those reads are characterized by two facts: $i.$ they have at most one
+difference with the best hit and $ii.$ the backward search depicted in
+Figure~\ref{fig:strategy} retrived only one sequence on each window.
+Individually, these facts are not uncommon in mismapped reads, but
+together, they leave little space for error.
 

### 2019-09-20 make_figure_mortal_kombat.R

@@ -23,7 +23,7 @@ lines(k, mem[8,], col="grey15", lwd=1.40)
 lines(k, mem[9,], col="grey10", lwd=1.45)
 lines(k, mem[10,], col="grey5", lwd=1.50)
 
-title(xlab="Size (nt)", ylab="Off-target rate (log10)",
+title(xlab="Read size (nt)", ylab="Off-target rate (log10)",
    col.lab="grey25", line=2.2)
 axis(side=1, cex.axis=.8, col="grey50", col.axis="grey25")
 axis(side=2, cex.axis=.8, col="grey50", col.axis="grey25")
@@ -48,7 +48,7 @@ lines(k, skip[8,], col="grey15", lwd=1.40)
 lines(k, skip[9,], col="grey10", lwd=1.45)
 lines(k, skip[10,], col="grey5", lwd=1.50)
 
-title(xlab="Size (nt)", ylab="Off-target rate (log10)",
+title(xlab="Read size (nt)", ylab="Off-target rate (log10)",
    col.lab="grey25", line=2.2)
 axis(side=1, cex.axis=.8, col="grey50", col.axis="grey25")
 axis(side=2, cex.axis=.8, col="grey50", col.axis="grey25")

### 2019-09-24 manuscript.tex
Add benchmark section and part of the discussion

@@
 The importance of faithfulness is recognized in the specifications of the
-SAM format \cite{1} that include a \emph{mapping quality} score. The
+SAM format \cite{1} that include a \emph{mapping quality} field. The
 standard defines it as $-10 \cdot \log_{10}Pr$\{mapping position is
-wrong\}, but some mappers use a qualitative scale (e.g., STAR), and
-some others do not compute it (e.g., GEM). As for the mappers that comply
-with the SAM standard, the scores are undocumented, causing
-puzzlement and frustration\footnote{http://www.acgt.me/blog/2015/3/17/more-madness-with-mapq-scores-aka-why-bioinformaticians-hate-poor-and-incomplete-software-documentation}.
+wrong\}, i.e. quality 20 stands for one error in 100 reads, quality 30 for
+one error in 1000 reads \textit{etc}. Some mappers disregard the standard
+and use a qualitative scale instead (e.g., STAR) while some others do not
+compute a mapping quality (e.g., GEM). As for the mappers that do comply
+with the SAM standard, the scores are undocumented, variable between
+mappers and versions, spreading puzzlement and frustration in the
+community\footnote{http://www.acgt.me/blog/2015/3/17/more-madness-with-mapq-scores-aka-why-bioinformaticians-hate-poor-and-incomplete-software-documentation}.
 
-Achieving faithful read mapping is a hard problem, for which this is
-presently no solution. Yet, this is an important challenge for the
-following reasons:
+The source of the issue is that there is presently no known method to
+properly estimate mapping quality. In other words, the the faithful
+mapping problem has no accepted solution. Yet, this is an important
+challenge for the following reasons:
 $i$ in many applications it is essential to know the risk associated with
@@
 
-Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text.
-Text \cite{2,3}.
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text.
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text.
-Text \cite{4}.
+Text. Text. Text. Text. Text. Text. Text. Text. Text \cite{2,3}.
+Text. Text. Text. Text. Text. Text. Text. Text. Text \cite{4}.
 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
 Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
@@
 \end{align}
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text
-(see Figure \ref{NAR-fig1}).
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
 Text. Text. Text. Text. Text. Text. Text.
@@
 Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text.
-
-\begin{figure}[t]
-\begin{center}
-\includegraphics{NAR-fig1.eps}
-\end{center}
-\caption{Caption for figure within column.}
-\label{NAR-fig1}
-\end{figure}
 
@@
 
-Figure~\ref{fig:mortal_kombat} shows the off-target probabilities computed
+\begin{figure*}[t]
+\begin{center}
+\includegraphics[scale=.6]{mortal_kombat.pdf}
+\end{center}
+\caption{Caption for wide figure over two columns.
+\textbf{(a)} Left figure.
+\textbf{(b)} Right figure (see (a)).
+}
+\label{fig_mortal_kombat}
+\end{figure*}
+
+Figure~\ref{fig_mortal_kombat} shows the off-target probabilities computed
 by Sesame. Counter-intuitively, the probability initially increases with
@@
 paralogues. Skip seeds are thus better suited for sensitive mapping in
-repeated sequences. Incidentally, this Figure~\ref{fig:mortal_kombat}
+repeated sequences. Incidentally, this Figure~\ref{fig_mortal_kombat}
 shows that it is suboptimal for a MEM-based mapper to all the candidate
@@
 
-Figure~\ref{fig:mortal_kombat} suggests that the performance of skip seeds
+Figure~\ref{fig_mortal_kombat} suggests that the performance of skip seeds
 is better than that of MEM seeds. However one has to bear in mind that we
@@
 
-\section{Estimating $N$ and $\mu$}
+\subsection{Estimating $N$ and $\mu$}
+\label{ref_Nmu}
 
@@
 
-The estimation strategy is depicted in Figure~\ref{fig:strategy}. The
+\begin{figure*}[t]
+\begin{center}
+\includegraphics{strategy.pdf}
+\end{center}
+\caption{Caption for wide figure over two columns.
+\textbf{(a)} Left figure.
+\textbf{(b)} Right figure (see (a)).
+}
+\label{fig_strategy}
+\end{figure*}
+
+The estimation strategy is depicted in Figure~\ref{fig_strategy}. The
 putative target is segmented in windows of 30 nucleotides overlapping by
@@
 
-\section{Super reads}
+\subsection{Super reads}
+\label{sec_super}
 
@@
 that a sub-population of them had mapping error rates below $10^{-5}$.
-This is surprising in regard of Figure~\ref{fig:mortal_kombat}a because in
+This is surprising in regard of Figure~\ref{fig_mortal_kombat}a because in
 a genome where half of the sequences are duplicated, the error rate should
@@
 
-Those reads are characterized by two facts: $i.$ they have at most one
-difference with the best hit and $ii.$ the backward search depicted in
-Figure~\ref{fig:strategy} retrived only one sequence on each window.
-Individually, these facts are not uncommon in mismapped reads, but
-together, they leave little space for error.
+Those reads are characterized by two facts: $i.$ they can be mapped witout
+mismatch and $ii.$ the backward search depicted in
+Figure~\ref{fig_strategy} retrieved only one sequence on each window.
+Individually, these conditions are not uncommon among mapping errors, but
+together they are exceedingly rare. Indeed, for a mapping error to occur,
+the target must have a paralogue, the read must be identical to the
+paralogue and the target must have been missed entirely while estimating
+$N$ and $\mu$.
+
+\begin{figure}[t]
+\begin{center}
+\includegraphics{super_reads.pdf}
+\end{center}
+\caption{Caption for figure within column.}
+\label{fig_super}
+\end{figure}
+
+As shown in Figure~\ref{fig_super}, the most likely scenario for a
+mapping error requires not just one, but two sequencing errors that match
+the paralogue exactly. In addition, these errors must be at specific
+positions of the read to mask the target. All other scenarios are even
+less likely, making conditions $i.$ and $ii.$ strong features of
+high-confidence mapping. Interestingly, those conditions are met on a
+substantial fraction of reads because the error rate is typically around
+1\% on short reads and 30-50\% of the sequences are unique in large
+eukaryotic genomes.
+
+Similar but more complex conditions hold when the read has 1 or 2
+mismatches against the best hit, so that it is often possible to reach
+high-confidence mapping when the target has no paralogue. Using such
+techniques, it is possible to map 50 bp reads with quality 70 in realistic
+sequencing conditions. This corresponds to one error in 10 million reads,
+i.e. at most handful per sequencing run. For longer reads, the maximum
+quality keeps increasing, but above 90 the differences become symbolic
+because the chances of observing a mapping error in a whole project become
+negligible.
+
+As commented earlier, mapping errors cannot occur if the target has no
+paralogue, so the key of super reads is to leverage the evidence that the
+target is a unique sequence. This depends on the knowledge of the
+reference genome, so the estimations are off on poorly assembled genomes.
+
+\subsection{Implementing a mapper}
+
+To evaluate the benefit of faithful mapping, we implemented a simple
+mapper using Sesame. The mapping policy is to extracts MEM seeds of size
+17 or more and to find the best scoring hit among the candidate loci by
+Needleman-Wunsch alignment\cite{1}. The only exception is that the mapper
+bails out if a MEM seeds has 300 or more hits in the genome, in which case
+it returns a candidate at random. This approach is exceptionally naive in
+comparison to modern mappers because it does not involve any refinement of
+the candidate set, using for instance seed chainig or re-seeding. But once
+the best candidate is found, the mapper estimates $N$ and $\mu$ using the
+procedure described in section~\ref{sec_Nmu} and computes the mapping
+quality with Sesame.
+
+We measured the performance of this strategy on the genomes of increasing
+complexity: \textit{Drosophila melanogaster} (the fruit fly), \textit{homo
+sapiens} (modern humans) and \textit{Pinus taeda} (a north-American
+species of pine). The basic features of the three genomes are summarized
+in Table~\ref{table_genomes}. Fly and human are model organisms with
+top-quality genome assembly. Pine is a non-model organism with a very
+large and complex genome. We used BWA MEM and Bowtie2 with default
+parameters to establish a baseline. The purpose of this benchmark is to
+evaluate the feasability of the strategy outlined above and not to
+advertise our prototype; it thus seemed inapropriate to run a
+comprehensive survey of all the availble options of each mapper.
 
@@
 \caption{This is a table caption}
-\label{table:01}%
+\label{table_genomes}%
 }{%
-\begin{tabular*}{\columnwidth}{@{}lllll@{}}
+\begin{tabular*}{\columnwidth}{@{}llrr}
 \toprule
-Col. head 1 & Col. head 2 & Col. head 3 & Col. head 4 & Col. head 5
-\\
-& (\%) & (s$^{-1}$) & (\%) & (s$^{-1}$)
-\\
+Organism & Reference & Size (Gbp) & Sequences \\
 \colrule
-Row 1 & Row 1 & Row 1 & -- & --
-\\
-Row 2 & Row 2 & Row 2 & Row 2 & Row 2
-\\
+\textit{D. melanogaster} & dm4/R6 & 0.15 & 1,870 \\
+\textit{H. sapiens} & hg38/GRCh38 & 3.27 & 455 \\
+\textit{P. taeda} & GCA\_000404065.3 & 22.50 & 1,760,464 \\
 \botrule
@@
 
-\subsection{Results subsection two}
+We did not pay any particular attention to the memory footpring of the
+mapper. Figure~\ref{fig_XX}a shows that the peak memory footprint is
+approximately twice as large as that of BWA and Bowtie2. One of the
+largest components of the FM index is the suffix array, which is
+compressed by a factor 32 in the case of BWA and Bowtie2 versus 16 in the
+case of our mapper. The reason for this choice is that the average memory
+on modern workstations has more than doubled since the release of BWA MEM
+and Bowtie2 around 2012, so we opted for an affordable boost in speed.
 
-Text.  Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text (see Table \ref{table:01}).
+Figure~\ref{fig_XX}b shows that the speed of our prototype mapper was in
+the same ballpark as that of BWA MEM and Bowtie2. The implementation
+compensates for the simplicity of the mapping policy by prioritizing the
+candidates loci, bailing out of the Needleman-Wunsch alignment as soon as
+a candidate appears to be sub-optimal, or even skipping the alignment
+whenever there is enough information at seeding stage to know that a
+candidate cannot be the best hit. Estimating $N$ and $\mu$ takes
+approximately x\% of the running time and computing probabilities with
+Sesame is negligible. This shows that the time required to compute
+accurate mapping qualities is not prohibitive and that faithful mapping is
+compatible with the time constraints associated with short read mapping.
 
-Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text (see Figure \ref{NAR-fig2}a).
+Having clarified this, our goal was of course to  evaluate the
+faithfulness of the mappers on the different problems. We included
+conditions far outside the expected, with error rates up to 10\%. The
+intent here was to stress the mappers to evaluate the robustness of the
+mappability scores. This is not entirely fair to BWA MEM and Bowtie2
+because they are optimized for a lower error rate, whereas we provided the
+error rate as a separate parameter for our mapper because it is required
+by Sesame. Nevertheless, it is still interesting to know the behavior of
+BWA MEM and Bowtie2 in stress conditions.
 
-Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+Figure~\ref{fig_YY} shows that our prototype mapper is faithful across all
+conditions. For long reads, the mapping quality is underestimated in the
+range below 20. Those reads map to repeated sequences where MEM seeds are
+particularly inaccurate according to Figure~\ref{fig_mortal_kombat}. Yet,
+this view appears to be somewhat pessimistic in practice. Yet, the true
+mapping quality of those reads remains below 20 and qualifies as low
+confidence in many applications.
 
-\begin{figure*}[t]
-\begin{center}
-\includegraphics{NAR-fig2.eps}
-\end{center}
-\caption{Caption for wide figure over two columns.
-\textbf{(a)} Left figure.
-\textbf{(b)} Right figure (see (a)).
-}
-\label{NAR-fig2}
-\end{figure*}
+Meanwhile, the faithfulness of BWA MEM and Bowtie2 is more variable and/or
+biased. The quality scores estimated by BWA MEM are strictly ascending but
+they are typically overstimated. For instance, the maximum quality 60 is
+typically off by two orders of magnitude, even on model genomes in
+realistc conditions. Still, the ascending nature of the score has two
+significant benefits for the users: first they can re-calibrate the
+quality scores by running simulations like this one, second they can be
+sure that reads with a higher mapping quality scores are indeed more
+likely to be correctly mapped. In comparison, the faithfulness profile of
+Bowtie2 shows less bias and more variance. The claimed mapping quality is
+overall in agreement with the empirical estimates, but the trend wiggles
+up and down. It is more difficult for the user to re-calibrate the trend
+or to select reads, but the benefit is that the claimed scores are
+relatively close to their real value.
 
-\subsection{Results subsection three}
+The maximum quality given by BWA MEM is 60 and that of Bowtie2 is 42. It
+is not completely apparent from Figure~\ref{fig_YY} that our prototype
+mapper goes much higher than either (the highest quality score in this
+benchmark was XX). Importantly, these extreme mapping qualities are not
+exaggerated: not a single read with quality above 60 is mapped at the
+wrong location in the whole benchmark (this represents more than XX reads
+without a single mistake). Those are mostly the super reads described in
+section~\ref{sec_super} and they represent a significant benefit of using
+Sesame.
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text.
+Finally, it is important to see whether the gain in faithfulness comes at
+the cost of accuracy. It is indeed questionable whether a MEM-based mapper
+can achieve good accuracy without re-seeding. Figure~\ref{fig_ZZ} shows
+that the overall accuracy of our prototype is comparable to that of BWA
+MEM and Bowtie2. Note that it is possible to fine tune BWA MEM and Bowtie2
+to reach higher accuracy (usually at the cost of computation time), but
+once again our goal here is only to show that it is possible to achieve
+faithfulness without sacrifices in speed or accuracy.
+
+Overall, blah blah.
 
@@
 
-\subsection{Discussion subsection one}
+\subsection{Computational strategies for mapping quality}
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text.
+Blah blah.
 
-\subsection{Discussion subsection two}
+\subsection{SMMFDP and more}
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text.
+The qualities of SMMFDP only come from faithfulness.
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
+It is interesting to observe that the accuracy of BWA MEM and our
+prototype are similar but they have entirely different origins. BWA MEM
+uses re-seeding to increase the sensitivity of the heuristic and discover
+candidates that escaped detection by MEM seeds. Our prototype gives up
+relatively fast but through faithfulness it ranks the reads in a way that
+optimizes the tradeoff.
 
-\subsection{Discussion subsection three}
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text.
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text.
-
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text.
+Similarly, the speed of our prototype comes in part from not compressing
+the suffix array as much as BWA MEM and Bowtie2, but more importantly from
+not trying too hard to map difficult reads. The rationale is that reads
+that are difficult to map end up with a poor mapping quality anyway, so
+extra efforts have little benefit. That said, it is necessary at times to
+push accuracy to its maximum and this strategy is inadapted. In such
+cases, we would switch to a more sensitive seeding method, such as skip
+seeds for instance, in order discover more candidates when there is
+evidence that the target has paralogues in the genome. However, our
+attempts with this strategy suggest that the benefit comes at a
+significant cost of computational time.
 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text.
+It's awesome. 'Nough said.
 
@@
 
-Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
-Text. Text. Text. Text.
+We acknowledge the financial support of the Spanish Ministry of Economy,
+Industry and Competitiveness (`Centro de Excelencia Severo Ochoa
+2013-2017', Plan Nacional BFU2012-37168), of the CERCA
+Programme~/~Generalitat de Catalunya, and of the European Research Council
+(Synergy Grant 609989). R.~C. was supported by the People Programme
+(Marie Curie Actions) of the European Union's Seventh Framework Programme
+(FP7/2007-2013) under REA grant agreement 608959. We also acknowledge
+support of the Spanish Ministry of Economy and Competitiveness (MEIC) to
+the EMBL partnership.
 

### 2019-09-24 make_figure_mortal_kombat.R

@@ -33,6 +33,8 @@ legend(x="bottomleft", lwd=c(1.05, 1.10, 1.15, 1.20, 1.25, 1.30,
    "grey35", "grey30", "grey25", "grey20", "grey15", "grey10", "grey5"),
    legend=c("1","5","10","20","50","100","200","400", "750","1500"),
    inset=.02, bg="white", box.col="white", text.col="grey25")
+legend(x="topright", inset=.02, bg="white", box.col="white",
+   legend="MEM seeds", text.col="grey25")
 
 plot(k, skip[1,], type="n",
    panel.first=grid(), ylim=ylim,
@@ -52,5 +54,8 @@ title(xlab="Read size (nt)", ylab="Off-target rate (log10)",
    col.lab="grey25", line=2.2)
 axis(side=1, cex.axis=.8, col="grey50", col.axis="grey25")
 axis(side=2, cex.axis=.8, col="grey50", col.axis="grey25")
+
+legend(x="topright", inset=.02, bg="white", box.col="white",
+   legend="Skip seeds", text.col="grey25")
 
 dev.off()
